BioTime

### 2019-04-17 biotime.Rmd
Search for common names with the appropriate column, give preference to species that match on the scientific column. Modify the unresolved function to gropu by the appropriate id (when do different columns are used in by_, sort will not be the appropriate unique grouping column.)

get_dupe_ids <- function(data){
  biotime_ids %>%
    distinct(acceptedNameUsageID, input, sort) %>%
    group_by(sort) %>% 
    filter(n()>1) %>% 
    ungroup()
}

unres <- get_dupe_ids(biotime_ids)
unres 
```

@@

##Elton Traits
Get id's for the Elton Bird trait data
```{r}
bird_ids <- by_name(unique(bird_trait$scientific), "itis") %>%
  bind_rows(by_common(unique(bird_trait$scientific), "itis")) %>%
  #filter(taxonRank == "species") %>% #only want ID's to species, since that's the level of the trait data
  drop_na(acceptedNameUsageID)
```

Are there any unresolved ids? Yes - just one, which is a synonym to two different accepted id's
```{r}
unres_trait <- get_dupe_ids(bird_ids) %>%
  left_join(bird_ids)

>>>>

get_dupe_ids <- function(data, orig_id){
  orig_id <- lazyeval::as_name(orig_id)

  data %>%
    distinct(acceptedNameUsageID, input, !!orig_id) %>%
    group_by(!!orig_id) %>% 
    filter(n()>1) %>% 
    ungroup()
}

unres <- get_dupe_ids(biotime_ids, "sort")
unres 
```

@@

##Elton Traits
Get id's for the Elton Bird trait data
```{r}
sci_names <-  by_name(unique(bird_trait$scientific), "itis") %>%
  drop_na(acceptedNameUsageID) %>%
  #get original specid so we can figure out how many don't have matches
  left_join(bird_trait %>% select(specid, scientific), by = c("input" = "scientific")) %>%
  mutate(match_type = "scientific")

com_names <- bird_trait %>% 
  filter(!specid %in% sci_names$specid) %>%
  pull(english) %>%
  unique() %>%
  by_common("itis") %>%
  #mutate(match_type = "common")
  #filter(taxonRank == "species") %>% #only want ID's to species, since that's the level of the trait data
  drop_na(acceptedNameUsageID) %>%
  left_join(bird_trait %>% select(specid, english), by = c("input" = "english"))%>%
  mutate(match_type = "common")

#there are both sci and common names, only want common name 
bird_ids <- bind_rows(sci_names, com_names)
```

Are there any unresolved ids? Yes - just one, which is a synonym to two different accepted id's
```{r}
unres_trait <- get_dupe_ids(bird_ids, "specid") %>%
  left_join(bird_ids)
